\MakeUppercase{Linear versus centred chromatic numbers}\thanks{This research was partly funded by NSERC.}

### 2022-05-30 lin-vs-cen.tex
Added affiliations

\title{\MakeUppercase{Linear versus centred chromatic numbers}\thanks{This research was partly funded by NSERC.}}
\author{Prosenjit~Bose, Vida~Dujmović, Hussein~Houdrouge, Mehrnoosh~Javarsineh, and Pat~Morin}

>>>>

\title{\MakeUppercase{Linear versus centred chromatic numbers}\thanks{This research was partly funded by NSERC.}}
\author{Prosenjit~Bose%
  \thanks{School of Computer Science, Carleton University},\,
  Vida~Dujmović%
  \thanks{Department of Computer Science and Electrical Engineering, University of Ottawa},\,\,
  Hussein~Houdrouge\footnotemark[2],\,
  Mehrnoosh~Javarsineh\footnotemark[2],\,
  and Pat~Morin\footnotemark[2]}
